\textsf{Are large language models superhuman chemists?}

### 2024-03-28 src/tex/ms.tex
[showyourwork] overleaf sync

\clearpage
\begin{abstract}
    Large language models (LLMs) have found widespread interest due to their abilities to process human language and to perform tasks they have not been explicitly trained on. 
    This is relevant for the chemical sciences, which face the problem of small and diverse datasets that are frequently in the form of text.
    LLMs have shown promise in addressing these issues and are increasingly being harnessed to predict chemical properties, optimize reactions, and even design and conduct experiments autonomously.

@@

    We curated more than 7,000 question-answer pairs for a wide array of chemical sciences subfields, evaluated leading evaluated leading open and closed-source LLMs, and found that the best models outperformed the best human chemists in our study on average. 
    The models, however, struggle with some chemical reasoning tasks that are easy for human experts and provide overconfident, misleading predictions, such as about chemicals' safety profiles.

>>>>

\clearpage
\begin{abstract}
    Large language models (LLMs) have gained widespread interest due to their ability to process human language and perform tasks they have not been explicitly trained on. 
    This is relevant for the chemical sciences, which face the problem of small and diverse datasets that are frequently in the form of text.
    LLMs have shown promise in addressing these issues and are increasingly being harnessed to predict chemical properties, optimize reactions, and even design and conduct experiments autonomously.

@@

    We curated more than 7,000 question-answer pairs for a wide array of chemical sciences subfields, evaluated leading open and closed-source LLMs, and found that the best models outperformed the best human chemists in our study on average. 
    The models, however, struggle with some chemical reasoning tasks that are easy for human experts and provide overconfident, misleading predictions, such as about chemicals' safety profiles.
